---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# materializer <img src="http://materializecss.com/res/materialize.svg" width="150">

[![Travis-CI Build Status](https://travis-ci.org/TuSKan/materializer.svg?branch=master)](https://travis-ci.org/TuSKan/materializer)

## Overview

The materializer is a set of packages that work in harmony because they share common data representations and API design. The __materializer__ package is designed to make it easy to install and load core packages from the tidyverse in a single command.

If you'd like to learn how to use the tidyverse effectively, the best place to start is [materialize](http://materializecss.com/).

## Installation

```{r eval = FALSE}
# Install from CRAN
install.packages("materializer")

# Or the development version from GitHub
# install.packages("devtools")
devtools::install_github("tuskan/materializer")
```
